---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# opiniontext

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## Overview
opiniontext is an ongoing project to build a data package containing text of
US Supreme Court opinions available publicly at SupremeCourt.gov. Text data is
to be made readily available in the form of text documents, csv, and R objects.
Csv and R objects outputted will contain the following columns:

* Case Name
* Date
* Opinion Type
* Author
* Text

## Installation

You can install the development version of opiniontext from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("JCRascal/opiniontext")
```

## Sample Usage

```{r, message = FALSE}
library(opiniontext)
library(tidytext)
library(dplyr)
library(ggplot2)

case_words <- opinions_2019 %>%
  unnest_tokens(word, text) %>%
  anti_join(get_stopwords(), by = "word") %>%
  count(author, word, sort = TRUE)
  
case_words <- case_words %>%
  group_by(author) %>%
  summarize(total = sum(n)) %>%
  right_join(case_words) %>%
  filter(nchar(word) > 2)

case_plot <- case_words %>%
  bind_tf_idf(word, author, n) %>%
  group_by(author) %>%
  slice_max(tf_idf, n = 15) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, tf_idf, author))

ggplot(case_plot, aes(word, tf_idf, fill = author)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~author, ncol = 2, scales = "free") +
  coord_flip() +
  scale_x_reordered()
  
```

## Data Collection Plan

* ~~Phase 1: Collect all available slip opinions for the 2019 session~~
* Phase 2: Collect all available slip opinions from 2014 session to present
* Phase 3: Collect official bound volumes


